How has the Brazilian Amazon been constructed as a problem? The economy, the environment, the people, and the nation in the presidential speeches since 1985

### 2022-06-13 Draft_June_2022/Full_draft_20220608.rmd
More changes with rmd

##### We are missing many observations for Collor from 1991 and 1992...
##### These are not in the repository for some reason...
##### Should we try and complete or should we at least disclose these in a footnote?

@@

         levels = c("Pure Economic Integration", "Pure Conservation", "Pure Social Development",

@@

                    "Social Economic", "Sovereign Conservation", "Economic, Social,\nand Conservation",
                    "Economic Sovereignty", "Social Conservation", "Other Mixed-types")),

@@

                                   |Pure Social Development|Pure Sovereignty", mx_cat) ~ "Pure-types",

@@

```{r Figure 2, fig.cap="Amazonian speeches by year", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
perc1 <- pop %>%
  count(amazon_speech, year) %>%
  group_by(year) %>%
  mutate(perc=n / sum(n)) %>%
  filter(amazon_speech == 1) %>% 
  select(c(perc, amazon_speech, year))
######## We have an issue with data here btw, 1992 only has 4 obs in the population... #######
######## Issue is with biblioteca presidencial, not with scarping btw ######
# summary(as.factor(pop$year))
# Simple plot
Amazon_year <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
  geom_line(color = "darkgreen") +
  scale_y_continuous(labels = percent_format()) +
  geom_text(aes(x = 1988.7, y = 0.34, label = "Chico Mendes"), size = 3) +
  geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
  geom_text(aes(x = 2009, y = 0.24, label = "Copenhagen Summit"), size = 3) +
  geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
  geom_vline(xintercept = c(1988.7, 1992, 2009, 2015),
             linetype = "dotted") +
  labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
       subtitle = "Sample composed by 6130 presidential speeches since 1985",
       caption = "",
       color='Y series') +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "bottom")
Amazon_year

# Word frequency year
popc <- filter(pop, amazon_speech == 1) %>%
  select(year, text) %>% 
  rename(doc_id = year)
popc$text <- stringr::str_replace_all(popc$text, "meio ambiente", "meioambiente")
popc$text <- stringr::str_replace_all(popc$text, "forcas armadas", "forcasarmadas")
popc$text <- stringr::str_replace_all(popc$text, "estados unidos", "estadosunidos")
popc$text <- stringr::str_replace_all(popc$text, "rio de janeiro", "riodejaneiro")
popc$text <- stringr::str_replace_all(popc$text, "direitos humanos", "direitoshumanos")
popc$text <- stringr::str_replace_all(popc$text, "rio grande do sul", "riograndedosul")
popc$text <- stringr::str_replace_all(popc$text, "copa do mundo", "copadomundo")
popc$text <- stringr::str_replace_all(popc$text, "sao paulo", "saopaulo")
popc$text <- stringr::str_replace_all(popc$text, "rio grande do norte", "riograndedonorte")
popc$text <- stringr::str_replace_all(popc$text, "floresta amazonica", "florestaamazonica")
popc$text <- stringr::str_replace_all(popc$text, "regiao amazonica", "regiaoamazonica")
popc$text <- stringr::str_replace_all(popc$text, "mato grosso|mato-grosso", "matogrosso")
popc$text <- stringr::str_replace_all(popc$text, "minas gerais", "minasgerais")
popc$text <- stringr::str_remove_all(popc$text, " [a-z] ")
popc$text <- tm::removeWords(tm::removePunctuation(popc$text),
                             c(tm::stopwords("pt"), 
                               "nao", "amazonas", "voce", "vao", "dar", "du",
                               "our", "amazonia", "governo", "amazonica", "ja", "aqui", "tambem",
                               "no", "hoje", "presidente", "governador", 
                               "sao", "voces", "ser", "bem", "la", "so", "desta", "porque",
                               "fazer", "quero", "ter", "vamos", "the", "of", "ha", "ai",
                               "ate", "vai", "dizer", "estao", "it", "ver", "r", "	it",
                               "cumprimentar", "gente", "estado", "querido", "queria",
                               "todos", "companheiro", "senhores", "alguns",
                               "companheiras", "companheiros", "companheira", "entao",
                               "senhor", "senhora", "agora", "senhores", "senhoras", "caro",
                               "grosso","ministro", "ministra", "josé", "jose",
                               "palacio", "planalto", "pronunciamento", "sobre",
                               "ministros", "luiz", "disse", "fizemos", "nesse",
                               "antonio", "vou", "eduardo braga", "pais", "coisa",
                               "então", "pouco", "pode", "sera", "dias",
                               "outro", "onde", "discurso", "parte", "fala",
                               "anos", "cada", "todo", "visite site", "disse",
                               "site secretaria", "minas gerais", "lula silva",
                               "inácio lula", "amapa", "bahia", "é", "lá", "et", "in",
                               "httpwwwimprensaplanaltogovbr", "secretaria", "visitesite",
                               "ta", "tudo", "pessoas", "falar", "neves", "tancredo",
                               "brasiliadf", "cardoso", "httpwwwinfoplanaltogovbr", 
                               "sip", "and", "to", "en", "des", "el", "le", "les", "dia",
                               "palavra dorsdne", "fernando henrique", "dorsdne eete",
                               "inacio lula", "lula silva", "inacio", "republica",
                               "quegente", "muitas vezes", "ainda", "realmente",
                               "assim", "possa", "coisas", "apenas", "acho", "ano",
                               "vez", "portanto", "todas", "questao", "lado", "outros",
                               "prezado", "vem", "sempre", "sarney", "luis", "serao", 
                               "tao", "meses", "quase", "diante", "brasil", "sendo",
                               "rsdneennoerqe", "brasil", "neste", "digo", "quase", 
                               "queremos", "nesse", "nessa", "mim", "eete", "obrigado", "muita"))
popc <- tm::VCorpus(tm::DataframeSource(popc))
popn <- tidytext::tidy(popc) %>%
  unnest_tokens(word, text) %>% 
  group_by(id, word) %>% 
  summarise(count = n()) %>% 
  arrange(-count) %>% 
  slice(1:10)
popn <- aggregate(popn$word, list(popn$id), paste, collapse=", ") %>% 
  rename(Year = "Group.1", Terms = "x")
tibble(popn)
##### LDA per year just in case
pop_dtm  <- DocumentTermMatrix(popc)
pop_lda <- topicmodels::LDA(pop_dtm, k = 10, control = list(seed = 1234))
pop_lday <- tidy(pop_lda, matrix = "gamma") %>%
  arrange(desc(gamma)) %>%
  group_by(document) %>%
  filter(row_number() %in% 1:1) %>% # get the top 3 topics per speaker
  arrange(document) %>%
  mutate(gamma = round(gamma, 1)) %>%
  distinct() %>% 
  rename (Year = document)
pop_10 <- tidy(pop_lda, matrix = "beta") %>%
  arrange(desc(beta)) %>%
  group_by(topic) %>%
  filter(row_number() %in% 1:10) %>%
  arrange(topic)
pop_10 <- aggregate(pop_10$term, list(pop_10$topic), paste, collapse=", ") %>%
  rename(topic = "Group.1", Terms = "x")
popt <- dplyr::left_join(pop_10, pop_lday, by = "topic") %>%
  select(Year, Terms) %>% 
  arrange(Year)
tibble(popt)

@@

```{r Figure 3, fig.cap="Pure types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
mmt1 <- ama_mx %>%
  filter(mx_cat2 == "Mixed-types") %>%
  count(mx_cat) %>%
  mutate(perc = n / sum(n)) # averages in relation to only mixed-types
mmt2 <- ama_mx %>%
  count(mx_cat)%>%
  mutate(perc = n / sum(n)) # averages in relation to full sample
pure_types_time <- ama_mx %>%
  count(mx_cat, mx_cat2, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(mx_cat2 == "Pure-types") %>% 
  ggplot(aes(x=as.numeric(year), y = perc, color = mx_cat)) +
  geom_smooth(aes(fill = mx_cat), se = FALSE, size = .5) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "", y = "", title ="Share of each pure type by year",
       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
       caption = "Curves in the plot were smoothed using loess method.") +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "bottom") +
  ggplot2::annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.40,
           fill = c("grey50", "ghostwhite", "grey50", "ghostwhite",
                    "grey50", "ghostwhite", "grey50", "ghostwhite"),
           alpha = 0.1) +
  ggplot2::annotate(geom = "text", x = hp$label, y = 0.01, vjus = 0.3, hjust = 0.3, angle = 25,
           label = hp$presid, alpha = 0.4)
pure_types_time
```

@@

```{r Figure 4, fig.cap="Mixed-types by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
mixed_types_presid <- ama_mx %>%
  count(president, mx_cat, mx_cat2) %>%
  group_by(president) %>%
  mutate(perc = n / sum(n)) %>%
  filter(mx_cat2 == "Mixed-types") %>%
  mutate(president = factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC",
                                                  "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
  ggplot(aes(x = president, y = perc, fill = mx_cat,
             label = scales::percent(perc, accuracy=.1))) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(size = 2, position = position_stack(vjust = .5)) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
  labs(x = "", y = "", title ="Share of each mixed type problem-constructions by president",
       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
       caption = "") +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "right")
mixed_types_presid
# mixed_types_time <- ama_mx %>%
#   count(mx_cat, mx_cat2, year) %>%
#   group_by(year) %>%
#   mutate(perc = n / sum(n),
#          perc = ifelse(perc == 1, 0.25, perc)) %>% # Issue with 1992 
#   filter(mx_cat2 == "Mixed-types") %>% 
#   ggplot(aes(x = as.numeric(year), y = perc, color = mx_cat)) +
#   geom_smooth(aes(fill = mx_cat), se = FALSE, size = .5) +
#   scale_y_continuous(labels = percent_format(accuracy = 1)) +
#   scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
#   labs(x = "", y = "", title ="Share of mixed type problem-constructions in time",
#        subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
#        caption = "") +
#   theme(panel.background = element_rect("white", "black", .5, "solid"),
#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
#         axis.text = element_text(color = "black", size = 10),
#         title = element_text(color = "black", size = 10, face = "bold"),
#         legend.title = element_blank(),
#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
#         legend.position = "bottom") +
#   annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.12,
#            fill = c("grey50", "ghostwhite", "grey50", "ghostwhite",
#                     "grey50", "ghostwhite", "grey50", "ghostwhite"),
#            alpha = 0.1) +
#   annotate(geom = "text", x = hp$label, y = 0.10, angle = 40,
#            label = hp$presid, alpha = 0.4)
# mixed_types_time
```

@@

```{r Figure 5, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
ama_model <- filter(ama_model, location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>%
  mutate(mx_cat = factor(mx_cat, levels = c("Pure Conservation", "Pure Economic Integration",
                                            "Pure Social Development", "Pure Sovereignty",
                                            "Economic Conservation", "Social Economic",
                                            "Sovereign Conservation", 
                                            "Economic, Social,\nand Conservation",
                                            "Economic Sovereignty", "Social Conservation", "Other")),
         con_vs_all = ifelse(mx_cat == "Pure Conservation", 1, 0),
         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
         sov_vs_all = ifelse(mx_cat == "Pure Sovereignty", 1, 0),
         location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul",
                                     location, ignore.case = TRUE), # minor coding issues to fix
                               "Non Amazonian States", location_cat),
         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
                               "International", location_cat), # minor coding issues to fix
         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
                                            location), "Amazonian Countries", location_cat),
                               levels = c("International", "Amazonian States",
                                          "Amazonian Countries", "Brasilia", "Non Amazonian States")))
# model
model <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
             family = binomial(link = 'logit'), data = ama_model)
# summary statistics
stargazer::stargazer(model, type = "text")
# Plot model
ama_model$predicted = predict(model, ama_model, type = "response")
ggplot(ama_model, aes(x = km_to_manaus, y = predicted)) + 
  geom_smooth(size = .5, color = "darkgreen") +
    labs(x = "Distance to Manaus (km)",
       y = "Environmental conservation",
       title = "Amazon constructions as an issue of pure environmental conservation\nin relation to distance to Manaus",
       subtitle = "Distance as a straight line from state, or country, capital to Manaus in kilometers",
       caption = "Curve in the plot is smoothed using loess method.") +
    theme(panel.background = element_rect("white", "black", .5, "solid"),
          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
          axis.text = element_text(color = "black", size = 10),
          title = element_text(color = "black", size = 10, face = "bold"),
          legend.title = element_blank(),
          plot.subtitle = element_text(color = "black", size = 9, face = "plain"))

>>>>

# Add a footnote about 1992 missing obs

@@

         levels = c("Pure Economic Integration", "Pure Conservation",
                    "Pure Social Development",

@@

                    "Social Economic", "Sovereign Conservation",
                    "Economic, Social,\nand Conservation",
                    "Economic Sovereignty", "Social Conservation",
                    "Other Mixed-types")),

@@

                                   |Pure Social Development|Pure Sovereignty",
                                   mx_cat) ~ "Pure-types",

@@

```{r Figure 2, fig.cap="Amazonian speeches by year", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
perc1 <- pop %>%
  count(amazon_speech, year) %>%
  group_by(year) %>%
  mutate(perc=n / sum(n)) %>%
  filter(amazon_speech == 1) %>% 
  select(c(perc, amazon_speech, year))
######## We have an issue with data here btw, 1992 only has 4 obs in the population... #######
######## Issue is with biblioteca presidencial, not with scarping btw ######
# summary(as.factor(pop$year))
# Simple plot
Amazon_year <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
  geom_line(color = "darkgreen") +
  scale_y_continuous(labels = percent_format()) +
  geom_text(aes(x = 1988.7, y = 0.34, label = "Chico Mendes"), size = 3) +
  geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
  geom_text(aes(x = 2009, y = 0.24, label = "Copenhagen Summit"), size = 3) +
  geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
  geom_vline(xintercept = c(1988.9, 1992, 2009, 2015),
             linetype = "dotted") +
  labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
       subtitle = "Sample composed by 6130 presidential speeches since 1985",
       caption = "",
       color='Y series') +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "bottom")
Amazon_year
```

@@

```{r Figure 3, fig.cap="Pure types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
pure_types_time <- ama_mx %>%
  count(mx_cat, mx_cat2, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(mx_cat2 == "Pure-types") %>% 
  ggplot(aes(x=as.numeric(year), y = perc, color = mx_cat)) +
  geom_smooth(aes(fill = mx_cat), se = FALSE, size = .5) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "", y = "", title ="Share of each pure type by year",
       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
       caption = "Curves in the plot were smoothed using loess method.") +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "bottom") +
  ggplot2::annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.40,
           fill = c("grey50", "ghostwhite", "grey50", "ghostwhite",
                    "grey50", "ghostwhite", "grey50", "ghostwhite"),
           alpha = 0.1) +
  ggplot2::annotate(geom = "text", x = hp$label, y = 0.01, vjus = 0.3, hjust = 0.3, angle = 25,
           label = hp$presid, alpha = 0.4)
pure_types_time
```

@@

```{r Figure 4, fig.cap="Mixed-types by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
mixed_types_presid <- ama_mx %>%
  count(president, mx_cat, mx_cat2) %>%
  group_by(president) %>%
  mutate(perc = n / sum(n)) %>%
  filter(mx_cat2 == "Mixed-types") %>%
  mutate(president = factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC",
                                                  "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
  ggplot(aes(x = president, y = perc, fill = mx_cat,
             label = scales::percent(perc, accuracy=.1))) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(size = 2, position = position_stack(vjust = .5)) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
  labs(x = "", y = "", title ="Share of each mixed type problem-constructions by president",
       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
       caption = "") +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "right")
mixed_types_presid
```

@@

```{r Figure 5, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
ama_model <- filter(ama_model, location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>%
  mutate(mx_cat = factor(mx_cat, levels = c("Pure Conservation", "Pure Economic Integration",
                                            "Pure Social Development", "Pure Sovereignty",
                                            "Economic Conservation", "Social Economic",
                                            "Sovereign Conservation", 
                                            "Economic, Social,\nand Conservation",
                                            "Economic Sovereignty", "Social Conservation", "Other")),
         con_vs_all = ifelse(mx_cat == "Pure Conservation", 1, 0),
         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
         sov_vs_all = ifelse(mx_cat == "Pure Sovereignty", 1, 0),
         location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul",
                                     location, ignore.case = TRUE), # minor coding issues to fix
                               "Non Amazonian States", location_cat),
         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
                               "International", location_cat), # minor coding issues to fix
         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
                                            location), "Amazonian Countries", location_cat),
                               levels = c("International", "Amazonian States",
                                          "Amazonian Countries", "Brasilia", "Non Amazonian States")))
# model
model <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
             family = binomial(link = 'logit'), data = ama_model)
# summary statistics
stargazer::stargazer(model, type = "text")
# Plot model
ama_model$predicted = predict(model, ama_model, type = "response")
ggplot(ama_model, aes(x = km_to_manaus, y = predicted)) + 
  geom_smooth(size = .5, color = "darkgreen") +
    labs(x = "Distance to Manaus (km)",
       y = "Environmental conservation",
       title = "Amazon constructions as an issue of pure environmental conservation\nin relation to distance to Manaus",
       subtitle = "Distance as a straight line from state or country's capital to Manaus in kilometers",
       caption = "Curve in the plot is smoothed using loess method.") +
    theme(panel.background = element_rect("white", "black", .5, "solid"),
          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
          axis.text = element_text(color = "black", size = 10),
          title = element_text(color = "black", size = 10, face = "bold"),
          legend.title = element_blank(),
          plot.subtitle = element_text(color = "black", size = 9, face = "plain"))
```

### 2022-06-13 Draft_May_2022/Full_draft_20220510.rmd
More changes with rmd

```{r Figure 4, fig.cap="Mixed-types by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
mixed_types_presid <- ama_mx %>%
  count(president, mx_cat, mx_cat2) %>%
  group_by(president) %>%
  mutate(perc = n / sum(n)) %>%
  filter(mx_cat2 == "Mixed-types") %>%
  mutate(president = factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC",
                                                  "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
  ggplot(aes(x = president, y = perc, fill = mx_cat,
             label = scales::percent(perc, accuracy=.1))) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(size = 2, position = position_stack(vjust = .5)) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
  labs(x = "", y = "", title ="Share of each mixed type problem-constructions by president",
       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
       caption = "") +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "right")
mixed_types_presid
# mixed_types_time <- ama_mx %>%
#   count(mx_cat, mx_cat2, year) %>%
#   group_by(year) %>%
#   mutate(perc = n / sum(n),
#          perc = ifelse(perc == 1, 0.25, perc)) %>% # Issue with 1992 
#   filter(mx_cat2 == "Mixed-types") %>% 
#   ggplot(aes(x = as.numeric(year), y = perc, color = mx_cat)) +
#   geom_smooth(aes(fill = mx_cat), se = FALSE, size = .5) +
#   scale_y_continuous(labels = percent_format(accuracy = 1)) +
#   scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
#   labs(x = "", y = "", title ="Share of mixed type problem-constructions in time",
#        subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
#        caption = "") +
#   theme(panel.background = element_rect("white", "black", .5, "solid"),
#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
#         axis.text = element_text(color = "black", size = 10),
#         title = element_text(color = "black", size = 10, face = "bold"),
#         legend.title = element_blank(),
#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
#         legend.position = "bottom") +
#   annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.12,
#            fill = c("grey50", "ghostwhite", "grey50", "ghostwhite",
#                     "grey50", "ghostwhite", "grey50", "ghostwhite"),
#            alpha = 0.1) +
#   annotate(geom = "text", x = hp$label, y = 0.10, angle = 40,
#            label = hp$presid, alpha = 0.4)
# mixed_types_time
```

>>>>

```{r Figure 4, fig.cap="Mixed-types by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
mixed_types_presid <- ama_mx %>%
  count(president, mx_cat, mx_cat2) %>%
  group_by(president) %>%
  mutate(perc = n / sum(n)) %>%
  filter(mx_cat2 == "Mixed-types") %>%
  mutate(president = factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC",
                                                  "Lula", "Dilma", "Temer", "Bolsonaro")))
  ggplot(aes(x = president, y = perc, fill = mx_cat,
             label = scales::percent(perc, accuracy=.1))) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(size = 2, position = position_stack(vjust = .5)) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
  labs(x = "", y = "", title ="Share of each mixed type problem-constructions by president",
       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
       caption = "") +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "right")
mixed_types_presid
# mixed_types_time <- ama_mx %>%
#   count(mx_cat, mx_cat2, year) %>%
#   group_by(year) %>%
#   mutate(perc = n / sum(n),
#          perc = ifelse(perc == 1, 0.25, perc)) %>% # Issue with 1992 
#   filter(mx_cat2 == "Mixed-types") %>% 
#   ggplot(aes(x = as.numeric(year), y = perc, color = mx_cat)) +
#   geom_smooth(aes(fill = mx_cat), se = FALSE, size = .5) +
#   scale_y_continuous(labels = percent_format(accuracy = 1)) +
#   scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
#   labs(x = "", y = "", title ="Share of mixed type problem-constructions in time",
#        subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
#        caption = "") +
#   theme(panel.background = element_rect("white", "black", .5, "solid"),
#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
#         axis.text = element_text(color = "black", size = 10),
#         title = element_text(color = "black", size = 10, face = "bold"),
#         legend.title = element_blank(),
#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
#         legend.position = "bottom") +
#   annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.12,
#            fill = c("grey50", "ghostwhite", "grey50", "ghostwhite",
#                     "grey50", "ghostwhite", "grey50", "ghostwhite"),
#            alpha = 0.1) +
#   annotate(geom = "text", x = hp$label, y = 0.10, angle = 40,
#            label = hp$presid, alpha = 0.4)
# mixed_types_time
```
